\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-20 doc/sw-system.tex
Added numeral I to system paper title, 'Gravitational' to CFHTLS paper title and adjusted short title. Closed #140
Abstract edits

We describe \SW, a novel gravitaional lens discovery service that yields samples
of high purity and completeness through crowd-sourced visual inspection.
Carefully produced colour composite images are displayed to volunteers via a
classification interface which records their estimates of the positions of
candidate lensed features. Simulated lenses, and expert-classified non-lenses,
are inserted into the image stream at random intervals; this training set is
used to give the volunteers feedback on their performance, and to estimate a
dynamically-updated probability for any given image to contain a lens. Low
probability systems are retired from the site periodically, concentrating the
sample towards a set of candidates. Having divided the 171 square degree
Canada-France-Hawaii Telescope Legacy Survey (\cfhtls)
imaging survey into some 430,000 overlapping 80 by 80 arcsecond tiles and
displayed them on the site, we were joined by around 37,000 volunteers who
contributed 10 million image classifications over the course of 8 months. The
sample was reduced to 3300 \StageOne candidates; these were then refined to
yield a sample of 90 \StageTwo detections, a sample we expect to be over 90\%
complete and 20\% pure at a threshold of 95\% classification probability. We
comment on the scalability of the \SW system to the wide field survey era.

>>>>

We describe \SW, a novel gravitaional lens discovery service that yields samples
of high purity and completeness through crowd-sourced visual inspection.
Carefully produced colour composite images are displayed to volunteers via a
classification interface which records their estimates of the positions of
candidate lensed features. Simulated lenses, and expert-classified images which lack lenses,
are inserted into the image stream at random intervals; this training set is
used to give the volunteers feedback on their performance, and to estimate a
dynamically-updated probability for any given image to contain a lens. Low
probability systems are retired from the site periodically, concentrating the
sample towards a set of candidates. Having divided the 171 square degree
Canada-France-Hawaii Telescope Legacy Survey (\cfhtls)
imaging survey into some 430,000 overlapping 80 by 80 arcsecond tiles and
displayed them on the site, we were joined by around 37,000 volunteers who
contributed 10 million image classifications over the course of 8 months. The
sample was reduced to 3300 \StageOne candidates; these were then refined to
yield a sample of 90 \StageTwo detections, a sample we expect to be over 90\%
complete and 20\% pure at a threshold of 95\% classification probability. We
comment on the scalability of the \SW system to the wide field survey era.
